The Skew-Normal Approximation of the Binomial Distribution

### 2010-12-25 project/paper/output.tex
Proofread new appendix section.

This approximation works best when the binomial is perfectly symmetrical, with
$p=0.5$. However as $p$ travels away from 0.5 in either direction, the binomial
becomes increasingly skewed, and one must either compensate by providing ever
larger values of $n$ or face growing inaccuracy. In these cases, the
skew-normal approximation can provide a better alternative.

@@

A quantitative method would be to compare the maximal absolute errors of our
two approximations, defined by \citet{mabs} as

@@

We leave you with a few practical resources:

@@

Appendix \ref{app:calc-sn-approx} demonstrates how to calculate the skew-normal
parameters by hand, for those who need an unusual combination not in the table.

Finally, for rapidly approximating many binomial distributions, the author's
Python library, which was used to compute all the values in this paper, is
freely available online:

@@

The left hand side of \eqref{eq:calculating-lambda} is a function of lambda;
let us denote it $f(\lambda)$. The right hand side is a constant in $n$ and
$p$; let us call it $k_{n,p}$. Our goal is to find a value of lambda that comes
within a certain margin of error, $e$. Since we are computing by hand, we will
take $e$ to be a modest 0.01.

@@

  \item \textit{Find $a,b$ such that $f(a) > k_{n,p} > f(b)$.}

@@

  \item \textit{Bisect $(a,b)$ until $f(c)$ is within $e$ of $k_{n,p}$.}

@@

\begin{equation*}
  \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} = 25 \cdot 0.1 - 2.2029 \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{2.3125}{\sqrt{1 + 2.3125^2}} = 0.8868.
\end{equation*}

>>>>

This approximation works best when the binomial is perfectly symmetrical, with
$p=0.5$. However as $p$ travels away from 0.5 in either direction, the binomial
becomes increasingly skewed, and one must either provide larger values of $n$
to compensate or face growing inaccuracy. In these cases, the skew-normal
approximation can provide a better alternative.

@@

A quantitative method of judging accuracy is comparing the maximal absolute
errors of our two approximations, defined by \citet{mabs} as

@@

We conclude our dicussion by offering the reader a few practical resources:

@@

For those with an unusual combination of $n$ and $p$ not in the table, Appendix
\ref{app:calc-sn-approx} demonstrates how to calculate the skew-normal
parameters by hand.

Finally, for rapidly approximating many binomial distributions, the author's
Python library, which was used to compute all values presented in this paper,
is freely available online:

@@

The left hand side of \eqref{eq:calculating-lambda} is a function of lambda;
let us denote it $f(\lambda)$. The right hand side is a constant in $n$ and
$p$; let us call it $k_{n,p}$. Our goal is to find a value of $\lambda$ such
that $f(\lambda)$ is within a certain margin of error, $e$, of $k_{n,p}$. Since
we are computing by hand, we will take $e$ to be a modest 0.01.

@@

  \item \textit{Find $a$ and $b$ such that $f(a) > k_{n,p} > f(b)$.}

@@

  \item \textit{Repeatedly bisect $(a,b)$ until $f(c)$ is within $e$ of $k_{n,p}$.}

@@

\begin{equation*}
  \mu = np - \sigma \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{\lambda}{\sqrt{1 + \lambda^2}} = 25 \cdot 0.1 - 2.2029 \cdot \sqrt{\frac{2}{\pi}} \cdot \frac{2.3125}{\sqrt{1 + 2.3125^2}} = 0.8867.
\end{equation*}
